### 2022-11-18 paper.Rmd
Figure number updated

```{r samplesize, include=F}
lavmodel <-  "Observe =~ item1 + item6 + item11 + item15 + item20 + item26 + item31 + item36
Describe =~ item2 + item7 + Ritem12 + Ritem16 + Ritem22 + item27 + item32 + item37
Awareness =~ Ritem5 + Ritem8 + Ritem13 + Ritem18 + Ritem23 + Ritem28 + Ritem34 + Ritem38
Nonjudge =~ Ritem3 + Ritem10 + Ritem14 + Ritem17 + Ritem25 + Ritem30+ Ritem35 + Ritem39
Nonreact =~ item4 + item9 + item19 + item21 + item24 + item29 + item33"

@@

```{r samplesizeIRT, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide', width=60}
library(SimDesign)
set.seed(222)
m <-  8 # item number
n <- c(50, 100, 200, 300, 400, 450, 500) # sample size
design <- as.data.frame(n)

@@

```{r apatheme, include=F}
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 40),
        axis.text.y = element_text(size = 40),
        axis.title.x = element_text(size = 40),
        axis.title.y = element_text(size = 40),
        plot.title = element_text(size = 40),
        legend.text = element_text(size = 40),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

## Participants
```{r data, include =F}
library(readxl)
data <- readRDS("ProcessedData/Bangla_FFMQ.rds")

@@

# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
desc_table <- Descriptives%>%
  tbl_summary(
    by = Gender,
    type = list(`Education Years` ~ 'continuous'),
    statistic = list(all_continuous() ~ "{mean} ({sd})", 
                     all_categorical() ~ "{n} ({p}%)"),

@@

```{r reliability-validity, include =F}

@@

```{r descriptives, include =F}
ob.m <- IRT  %>% 
  dplyr::select(item1 , item6 , item11 , item15 , item20 , item26 , item31 , item36)

des.m <- IRT  %>% 
  dplyr::select(item2 , item7 , Ritem12 , Ritem16 , Ritem22 , item27 , item32 , item37)

actw.m <- IRT  %>% 
  dplyr::select(Ritem5, Ritem8, Ritem13, Ritem18, Ritem23, Ritem28, Ritem34, Ritem38)

nj.m <- IRT  %>% 
  dplyr::select(Ritem3 , Ritem10 , Ritem14 , Ritem17 , Ritem25 , Ritem30, Ritem35,  Ritem39)

nr.m <- IRT %>% 
  dplyr::select(item4 , item9 , item19 , item21 , item24 , item29 , item33)

des.ob <- tabledown::des.tab(ob.m)

des.des <- tabledown::des.tab(des.m )
des.actw <- tabledown::des.tab(actw.m)
des.nj <- tabledown::des.tab(nj.m )
des.nr <- tabledown::des.tab(nr.m )

descriptives <- rbind(des.ob,des.des,des.actw,des.nj,des.nr)

mvn.observe <- MVN::mvn(ob.m, mvnTest = "mardia" )
mvn.describe <- MVN::mvn(des.m, mvnTest = "mardia" )
mvn.actware <- MVN::mvn(actw.m, mvnTest = "mardia" )
mvn.nj <- MVN::mvn(nj.m, mvnTest = "mardia" )
mvn.nr <- MVN::mvn(nr.m, mvnTest = "mardia" )

ob.icor <-as.data.frame(as.numeric(des.ob$Corrected.item.total.correlation))
des.icor <-as.data.frame(as.numeric(des.des$Corrected.item.total.correlation))
actw.icor <-as.data.frame(as.numeric(des.actw$Corrected.item.total.correlation))
nj.icor <-as.data.frame(as.numeric(des.nj$Corrected.item.total.correlation))
nr.icor <-as.data.frame(as.numeric(des.nr$Corrected.item.total.correlation))

@@

```{r tabDes, results='asis'}
apa_table(descriptives, caption = "Descriptive Statistics")
```

@@

```{r Unidim, include =F}
tab1 <-  tabledown::cfa.tab.multi(fit.ob, fit.des, fit.des.mi,   robust = F)
tab2 <- tabledown::cfa.tab.multi(fit.aw, fit.nonj, fit.nonj.mi,robust = F)
tab3 <- tabledown::cfa.tab(fit.nonr,robust = F)

@@

```{r Unitab, results='asis'}
apa_table(unidimension2, caption = "Unidimensionality of each Mindfulness facet")
```

@@

```{r OCC-irt3,  include=FALSE}
#general inspection of Option charecteristics curve based on the third iteration

@@

```{r ggitem-info-all-plots}
#We used all item-info plot in the manuscript
#Observe
info.item1 <- ggiteminfo(observe.fit.2,1,6)+ggtitle("Obs:item01")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+ geom_area(fill =  "#E64B3599")

info.item28 <- ggiteminfo(awareness.fit.2,6,6)+ggtitle("Actw:item28")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item3 <- ggiteminfo(nonjudge.fit.2,1,6)+ggtitle("Nonj:item03")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item10 <- ggiteminfo(nonjudge.fit.2,2,6)+ggtitle("Nonj:item10")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item17 <- ggiteminfo(nonjudge.fit.2,3,6)+ggtitle("Nonj:item17")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item25 <- ggiteminfo(nonjudge.fit.2,4,6)+ggtitle("Nonj:item25")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item30 <- ggiteminfo(nonjudge.fit.2,5,6)+ggtitle("Nonj:item30")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item35 <- ggiteminfo(nonjudge.fit.2,6,6)+ggtitle("Nonj:item35")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

info.item39 <- ggiteminfo(nonjudge.fit.2,7,6)+ggtitle("Nonj:item39")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(aes(fill =  "#3C548899"))

ggsave("Figures/Fig3.png",all_info , units = "mm", width = 174, height = 234, dpi = 600, bg = "white")

```{r problematic-icc, include=F}
#Publication quality OCC
library(ggsci)

@@

# 38, 22, 39, 3, and 17

@@

item26.icc <- ggicc(observe.fit.2,6,6)+ggtitle("Representative OCC: item26")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

@@

ggsave("Figures/Fig4.tiff",problematic_icc_2 , units = "mm", width = 174, height = 117, dpi = 600, bg = "white")

@@

@@

```{r fig-occ, fig.cap= "Option Charecteristics curve (A) Observe, (B) Describe, (C)Act with awareness, (D)Nonjudgement, (E) Nonreact" , results= 'asis'}
knitr::include_graphics('Figures/Fig6.png', dpi =600)

@@

```{r personfitd, include=FALSE}
#Person Fit ####

@@

ggsave("Figures/Fig5.png",personfit, units = "mm", width = 174, height = 117, dpi = 600, bg = "white")

@@

```{r person-fit, fig.cap= "Person Fit of the Five fitted Models (A) Observe, (B) Describe, (C)Act with awareness, (D)Nonjudgement, (E) Nonreact" , results= 'asis'}
knitr::include_graphics('Figures/Fig5.png', dpi =600)

@@

@@

TIC.plot <- cowplot::plot_grid(observe.TIC.1,describe.TIC.1, awareness.TIC.1,
                                   nonjudge.TIC.1,nonreact.TIC.1,
                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 40,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/Fig6.png",TIC.plot, units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

knitr::include_graphics('Figures/Fig6.png', dpi =600)
```

```{r con-rel, include =F}
#conditional reliability
observe_reliability <- tabledown::ggreliability(observe.refit.2, observe.fit.3)+apatheme+geom_area()+theme(legend.position = "none")+
  aes(fill =  "#E64B3599")+scale_fill_identity() +xlab(expression(theta)) + 
  ylab(expression(I(theta)))

@@

reliability_plot <- cowplot::plot_grid(observe_reliability,describe_reliability, awareness_reliability,
                                   nonjudge_reliability,nonreact_reliability,
                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 40,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")

ggsave("Figures/Fig7.png",reliability_plot, units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

```{r conrel-fig, fig.cap= "Conditional Reliability plots: (A) Observe, (B) Describe, (C)Act with awareness", results='asis'}
knitr::include_graphics('Figures/Fig7.png', dpi =600)

@@

```{r saveWrightmao, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
jpeg("Figures/wp.png", width = 800, height = 750)
WrightMap::wrightMap(estimation, threshold, 
          item.prop = 0.65,
          main.title = "Five Facet Mindfulness Questionnaire",
          dim.names = c("Observe", "Describe", "Actware", "Nonjudge", "Nonreact"),
          thr.sym.col.fg = itemlevelcolors,
          thr.sym.col.bg = itemlevelcolors,
          vertLines = TRUE,
          show.thr.lab = F,
          dim.color = brewer.pal(5, "Set3"),
          label.items.srt = 45
          )

@@

knitr::include_graphics('Figures/wp.png')
```

@@

p1 <- ggplot(totalscore_1, aes(x=Theta, y=totalscore))+geom_line()+xlab(expression(theta))+ylab(expression(T(theta)))+theme(legend.position = "none")+geom_segment(aes(x=0,xend=-Inf,y=perc[2],yend=perc[2]))+
  geom_segment(aes(x=0,xend=0,y=-Inf,yend=perc[2]))+
  geom_text(data = tibble (x = -.40, y = perc[2]+.8),
            aes(x=x, y = y,  label = perc[2]), inherit.aes = FALSE, size = 12)

@@

                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 40,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/score.png",score.plot , units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

#Fit the model
esem_fit_higher_order <- lavaan::cfa(esem_model_higher_order, fscores, ordered = names(fscores),estimator = "WLSMV", mimic = "Mplus", std.lv=T)

@@

@@

#Find the referent item for each factor
referents_higher_order <- find_referents(esem_tareget_efa_higher_order , factor_names = c("Orientation To Experience","Self-regulated Attention"))

@@

#Fit the model
esem_fit_higher_order <- lavaan::cfa(esem_model_higher_order, fscores, ordered = names(fscores),estimator = "WLSMV", mimic = "Mplus", std.lv=T)

@@

#  rel.esm_ho <- reliability(esem_fit_higher_order , return.total = TRUE)
# # 
# # rel.esm_ho.m <- rel.esm_ho[4,]
# Total scale omega is .74. each factors alpha f1=.54, f2 =.54. omega F1=.44, F2=.30.

>>>>

```{r samplesize, include=F}
#Simulation to estimate required sample size for CFA

lavmodel <-  "Observe =~ item1 + item6 + item11 + item15 + item20 + item26 + item31 + item36
Describe =~ item2 + item7 + Ritem12 + Ritem16 + Ritem22 + item27 + item32 + item37
Awareness =~ Ritem5 + Ritem8 + Ritem13 + Ritem18 + Ritem23 + Ritem28 + Ritem34 + Ritem38
Nonjudge =~ Ritem3 + Ritem10 + Ritem14 + Ritem17 + Ritem25 + Ritem30+ Ritem35 + Ritem39
Nonreact =~ item4 + item9 + item19 + item21 + item24 + item29 + item33"

@@

```{r samplesizeIRT, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide', width=60}

#Simulation to estimate required sample size for CFA

library(SimDesign)
set.seed(222)
m <-  8 # item number
n <- c(50, 100, 200, 300, 400, 450, 500) # sample size
design <- as.data.frame(n)

@@

```{r apatheme, include=F}
#Create apatheme for the plots
apatheme=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 40),
        axis.text.y = element_text(size = 40),
        axis.title.x = element_text(size = 40),
        axis.title.y = element_text(size = 40),
        plot.title = element_text(size = 40),
        legend.text = element_text(size = 40),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

## Participants
```{r data, include =F}
#This chunk uploads the data to the system and devides the data for  descriptives, IRT, and validity analysis
library(readxl)
data <- readRDS("ProcessedData/Bangla_FFMQ.rds")

@@

# create descriptive table for the demographic vars  with gtsummary
desc_table <- Descriptives%>%
  tbl_summary(
    by = Gender,
    type = list(`Education Years` ~ 'continuous'),
    statistic = list(all_continuous() ~ "{mean} ({sd})", 
                     all_categorical() ~ "{n} ({p}%)"),

@@

```{r reliability-validity, include =F}
#This chunks calculates reliability of the constructs used for validation of BFFMQ

@@

```{r descriptives, include =F}
#This chunks holds the codes for descriptives analysis
descriptives <- IRT #load data

#Remane for sorting purpose!
names(descriptives)[names(descriptives) == "item1"] <- "item01"
names(descriptives)[names(descriptives) == "item2"] <- "item02"
names(descriptives)[names(descriptives) == "Ritem3"] <- "item03"
names(descriptives)[names(descriptives) == "item4"] <- "item04"
names(descriptives)[names(descriptives) == "Ritem5"] <- "item05"
names(descriptives)[names(descriptives) == "item6"] <- "item06"
names(descriptives)[names(descriptives) == "item7"] <- "item07"
names(descriptives)[names(descriptives) == "Ritem8"] <- "item08"
names(descriptives)[names(descriptives) == "item9"] <- "item09"
names(descriptives)[names(descriptives) == "Ritem10"] <- "item10"
names(descriptives)[names(descriptives) == "Ritem12"] <- "item12"
names(descriptives)[names(descriptives) == "Ritem13"] <- "item13"
names(descriptives)[names(descriptives) == "Ritem14"] <- "item14"
names(descriptives)[names(descriptives) == "Ritem16"] <- "item16"
names(descriptives)[names(descriptives) == "Ritem17"] <- "item17"
names(descriptives)[names(descriptives) == "Ritem18"] <- "item18"
names(descriptives)[names(descriptives) == "Ritem22"] <- "item22"
names(descriptives)[names(descriptives) == "Ritem23"] <- "item23"
names(descriptives)[names(descriptives) == "Ritem25"] <- "item25"
names(descriptives)[names(descriptives) == "Ritem28"] <- "item28"
names(descriptives)[names(descriptives) == "Ritem30"] <- "item30"
names(descriptives)[names(descriptives) == "Ritem34"] <- "item34"
names(descriptives)[names(descriptives) == "Ritem35"] <- "item35"
names(descriptives)[names(descriptives) == "Ritem38"] <- "item38"
names(descriptives)[names(descriptives) == "Ritem39"] <- "item39"

#Setting data frame for the five factes
ob.m <- descriptives  %>% 
  dplyr::select(item01 , item06 , item11 , item15 , item20 , item26 , item31 , item36)

des.m <- descriptives  %>% 
  dplyr::select(item02 , item07 , item12 , item16 , item22 , item27 , item32 , item37)

actw.m <- descriptives  %>% 
  dplyr::select(item05, item08, item13, item18, item23, item28, item34, item38)

nj.m <- descriptives  %>% 
  dplyr::select(item03 , item10 , item14 , item17 , item25 , item30, item35,  item39)

nr.m <- descriptives %>% 
  dplyr::select(item04 , item09 , item19 , item21 , item24 , item29 , item33)

#Descriptives using tab des
des.ob <- tabledown::des.tab(ob.m)
des.des <- tabledown::des.tab(des.m )
des.actw <- tabledown::des.tab(actw.m)
des.nj <- tabledown::des.tab(nj.m )
des.nr <- tabledown::des.tab(nr.m )

#Join all facets
descriptives_tab <- rbind(des.ob,des.des,des.actw,des.nj,des.nr)

#Mardia test of multivariate normality
mvn.observe <- MVN::mvn(ob.m, mvnTest = "mardia" )
mvn.describe <- MVN::mvn(des.m, mvnTest = "mardia" )
mvn.actware <- MVN::mvn(actw.m, mvnTest = "mardia" )
mvn.nj <- MVN::mvn(nj.m, mvnTest = "mardia" )
mvn.nr <- MVN::mvn(nr.m, mvnTest = "mardia" )

#Item-total correlations
ob.icor <-as.data.frame(as.numeric(des.ob$Corrected.item.total.correlation))
des.icor <-as.data.frame(as.numeric(des.des$Corrected.item.total.correlation))
actw.icor <-as.data.frame(as.numeric(des.actw$Corrected.item.total.correlation))
nj.icor <-as.data.frame(as.numeric(des.nj$Corrected.item.total.correlation))
nr.icor <-as.data.frame(as.numeric(des.nr$Corrected.item.total.correlation))

```{r fig2data, include=FALSE}
#This chunk summarizes the data for Fig2
gt.data <- descriptives  %>% 
  dplyr::select(item01 , item06 , item11 , item15 , item20 , item26 , item31 , item36,item02 , item07 , item12 , item16 , item22 , item27 , item32 , item37,item05, item08, item13, item18, item23, item28, item34, item38, item03 , item10 , item14 , item17 , item25 , item30, item35,  item39,item04 , item09 , item19 , item21 , item24 , item29 , item33)

#Recode key
recod_code <- c( "1" = "Never or very rarely true", "2" = "Rarely true", "3"= "Sometimes true","4" = "Often true",
                 "5" = "Very often or always true")

#Data for gtExtras
full.tab <- tabledown::gt_tab(gt.data,recod_code )

#Arrange the data
full.tab_1 <- full.tab[, c(1,8,11,12,13,7,14,16,17,15,18)]
full.tab_des <- inner_join(full.tab_1, descriptives_tab, by = "Items") #descriptives_tab is used to get the facet wise values.
full.tab_2 <- full.tab_des[, c(1,12,13,4,17,6:11)]
#Set colnames
colnames(full.tab_2 ) <- c("Items", "Mean", "SD","S-W Statistics","Item-Total Correlation", "dens_data","Never or very rarely true","Rarely true","Sometimes true","Often true",  "Very often or always true" )

```{r Fig2,  include=FALSE}
#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA+CFA);

full.tab_3 <- full.tab_2 %>% gt() #Converts to gt object

full.tab_3 %>% 
# histogram and density plots
  # gtExtras::gt_plt_dist(
  #   hist_data,
  #   type = "histogram",
  #   line_color = "black", 
  #   fill_color = "#00A08799",
  #   bw = 1,
  #   same_limit = TRUE)%>%
  gtExtras::gt_plt_dist(
    dens_data,
    type = "density",
    line_color = "black", 
    fill_color = "#00A08799",
    bw = 0.75,
    same_limit = TRUE
  )%>%
# format decimals
  # fmt_number(columns = Mean:SD, decimals = 1) %>%
# header
  tab_header(
    title = md("Summary Descriptives (n=532)"),
    ) %>% #create groups of columns

  tab_spanner(
    label = "Summary Statistics",
    columns = Mean:`Item-Total Correlation`
  ) %>%
  tab_spanner(
    label = "Graphics",
    columns = dens_data
  ) %>% 
  tab_spanner(
    label = "Response Pattern",
    columns = `Never or very rarely true`:`Very often or always true`
  ) %>%
     tab_footnote(
     footnote = md("**Shapiro–Wilk test; *p<0.001**"),
     locations = cells_column_labels(columns = `S-W Statistics`)
  ) %>% 
  tab_footnote(
     footnote = md("**%(n)**"),
     locations = cells_column_labels(columns = `Never or very rarely true`:`Very often or always true`)
  ) %>% 
# change column names to appear in the table
cols_label(
  Items = ("Items"),
  Mean = ("Mean"),
  SD = ("SD"),
  `Item-Total Correlation` = ("Item-Total Correlation"),
  `S-W Statistics` = ("SW"),
  # hist_data = "Histogram",
  dens_data = "Density"
)  %>% 
# set alignment as per wish
  cols_align(
    align = "center",
    columns = Mean: `Very often or always true`
  ) %>%
  opt_align_table_header(align = "left") %>%
# add coloured dots and lines on the first column
  gt_plt_dot(
    Mean,
    Items,
    palette = "ggthemes::fivethirtyeight"
  ) %>% tab_options(
    table.font.size = px(30L)) %>%
   tab_row_group(
      label = md("**Nonreact**"),
      rows = c(4 ,9,19,21,24,29,33)
        ) %>%
  tab_row_group(
      label = md("**Nonjudge**"),
      rows = c(3 ,10 ,14 ,17 ,25 ,30,35,39)
        ) %>%
  tab_row_group(
      label = md("**Awareness**"),
      rows = c(5 ,8 ,13 ,18 ,23 ,28 ,34 ,38)
        ) %>%
  tab_row_group(
      label = md("**Describe**"),
      rows = c(2 ,7 ,12 ,16 ,22 ,27 ,32 ,37)
        ) %>%
  tab_row_group(
      label = md("**Observe**"),
      rows = c(1 ,6 ,11 ,15 ,20 ,26 ,31 ,36)
        ) %>%
 gtsave("Figures/PNG/Fig2.png", vwidth = 3000)

@@

```{r tabDes, results='asis'}
#Prints the descriptives in the manuscript
apa_table(descriptives, caption = "Descriptive Statistics")
```

@@

```{r Unidim, include =F}

#Creates table 1 in the manuscript
tab1 <-  tabledown::cfa.tab.multi(fit.ob, fit.des, fit.des.mi,   robust = F)
tab2 <- tabledown::cfa.tab.multi(fit.aw, fit.nonj, fit.nonj.mi,robust = F)
tab3 <- tabledown::cfa.tab(fit.nonr,robust = F)

@@

```{r Unitab, results='asis'}
#Table1
apa_table(unidimension2, caption = "Unidimensionality of each Mindfulness facet")
```

@@

```{r mirtocc,  include=FALSE}
#general inspection of Option charecteristics curve based on the third iteration

@@

```{r Fig3, include=F}
#Code for fig3 one ideal OCC and 5 promlematic OCC
library(ggsci)

@@

# 38, 22, 39, 3, and 17: problematic items

@@

#item 26 representative OCC
item26.icc <- ggicc(observe.fit.2,6,6)+ggtitle("Representative OCC: item26")+apatheme+scale_color_npg()+
  scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")

@@

ggsave("Figures/PNG/Fig3.png",problematic_icc_2 , units = "mm", width = 174, height = 117, dpi = 600, bg = "white")

@@

```{r Fig4, include=F}
#We used all item-info plot (Fig4) in the manuscript
#Observe
info.item1 <- ggiteminfo(observe.fit.2,1,6)+ggtitle("Obs:item01")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+ geom_area(fill =  "#E64B3599")

info.item28 <- ggiteminfo(awareness.fit.2,6,6)+ggtitle("Actw:item28")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1.2))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#00A08799")

info.item3 <- ggiteminfo(nonjudge.fit.2,1,6)+ggtitle("Nonj:item03")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#3C548899")

info.item10 <- ggiteminfo(nonjudge.fit.2,2,6)+ggtitle("Nonj:item10")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#3C548899")

info.item17 <- ggiteminfo(nonjudge.fit.2,3,6)+ggtitle("Nonj:item17")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#3C548899")

info.item25 <- ggiteminfo(nonjudge.fit.2,4,6)+ggtitle("Nonj:item25")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#3C548899")

info.item30 <- ggiteminfo(nonjudge.fit.2,5,6)+ggtitle("Nonj:item30")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#3C548899")

info.item35 <- ggiteminfo(nonjudge.fit.2,6,6)+ggtitle("Nonj:item35")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#3C548899")

info.item39 <- ggiteminfo(nonjudge.fit.2,7,6)+ggtitle("Nonj:item39")+apatheme+scale_color_npg()+
scale_y_continuous(breaks=c(0,.5,1), limits = c(0, 1))+theme(legend.position="none")+
  xlab(expression(theta)) + 
  ylab(expression(I(theta)))+geom_hline(yintercept = .20, linetype="dashed")+geom_area(fill =  "#3C548899")

ggsave("Figures/PNG/Fig4.png",all_info , units = "mm", width = 174, height = 234, dpi = 600, bg = "white")
ggsave("Figures/Fig3.tiff",all_info , units = "mm", width = 174, height = 234, dpi = 600, bg = "white")

@@

```{r fig-occ, fig.cap= "Option Charecteristics curve (A) Observe, (B) Describe, (C)Act with awareness, (D)Nonjudgement, (E) Nonreact" , results= 'asis'}
knitr::include_graphics('Figures/PNG/Fig3.png', dpi =600)

@@

```{r Fig5, include=FALSE}
#Person Fit ####

@@

ggsave("Figures/PNG/Fig5.png",personfit, units = "mm", width = 174, height = 117, dpi = 600, bg = "white")

@@

```{r person-fit, fig.cap= "Person Fit of the Five fitted Models (A) Observe, (B) Describe, (C)Act with awareness, (D)Nonjudgement, (E) Nonreact" , results= 'asis'}
knitr::include_graphics('Figures/PNG/Fig5.png', dpi =600)

@@

```{r apathemelong, include=F}
apatheme_large=theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        #text=element_text(family = "Helvetica"),
        axis.text.x = element_text(size = 90),
        axis.text.y = element_text(size = 90),
        axis.title.x = element_text(size = 90),
        axis.title.y = element_text(size = 90),
        plot.title = element_text(size = 90),
        legend.text = element_text(size = 90),
        legend.title=element_blank(),
        axis.line.x = element_line(color='black'),
        axis.line.y = element_line(color='black'),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 1))
```

@@

TIC.plot <- cowplot::plot_grid(observe.TIC.1,describe.TIC.1, awareness.TIC.1,
                                   nonjudge.TIC.1,nonreact.TIC.1,
                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 90,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Figures/PNG/Fig6.png",TIC.plot, units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

knitr::include_graphics('Figures/PNG/Fig6.png', dpi =600)
```

```{r Fig7, include =F}
#conditional reliability
observe_reliability <- tabledown::ggreliability(observe.refit.2, observe.fit.3)+apatheme+geom_area()+theme(legend.position = "none")+
  aes(fill =  "#E64B3599")+scale_fill_identity() +xlab(expression(theta)) + 
  ylab(expression(I(theta)))

@@

reliability_plot <- cowplot::plot_grid(observe_reliability,describe_reliability, awareness_reliability,
                                   nonjudge_reliability,nonreact_reliability,
                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 80,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")

ggsave("Figures/PNG/Fig7.png",reliability_plot, units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

```{r conrel-fig, fig.cap= "Conditional Reliability plots: (A) Observe, (B) Describe, (C)Act with awareness", results='asis'}
knitr::include_graphics('Figures/PNG/Fig7.png', dpi =600)

@@

```{r Fig8, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
jpeg("Figures/PNG/Fig8.png", width = 800, height = 750)
WrightMap::wrightMap(estimation, threshold, 
          item.prop = 0.65,
          main.title = "Five Facet Mindfulness Questionnaire",
          dim.names = c("Observe", "Describe", "Actware", "Nonjudge", "Nonreact"),
          thr.sym.col.fg = itemlevelcolors,
          thr.sym.col.bg = itemlevelcolors,
          vertLines = TRUE,
          show.thr.lab = F,
          dim.color = brewer.pal(5, "Set3"),
          label.items.srt = 45
          )

@@

knitr::include_graphics('Figures/PNG/Fig8.png')
```

@@

p1 <- ggplot(totalscore_1, aes(x=Theta, y=totalscore))+geom_line()+xlab(expression(theta))+ylab(expression(T(theta)))+theme(legend.position = "none")+geom_segment(aes(x=0,xend=-Inf,y=perc[2],yend=perc[2]))+
  geom_segment(aes(x=0,xend=0,y=-Inf,yend=perc[2]))+
  geom_text(data = tibble (x = -.60, y = perc[2]+.8),
            aes(x=x, y = y,  label = perc[2]), inherit.aes = FALSE, size = 12)

@@

                   labels = "auto",
                     align="v",
                     ncol = 3,
                     label_size = 40,
                     # label_fontfamily = "Arial",
                     label_fontface = "plain")
# ggsave("Figures/score.png",score.plot , units = "mm", width = 174, height = 150, dpi = 600, bg = "white")

@@

#Fit the model
esem_fit_higher_order <- lavaan::cfa(esem_model_higher_order, fscores,estimator = "WLSMV", mimic = "Mplus", std.lv=T)

@@

#Rename variables
names(fscores ) <- c("Obs", "Des", "Actw", "Nonj", "Nonr")

@@

#Find the referent item for each factor
referents_higher_order <- find_referents(esem_tareget_efa_higher_order , factor_names = c("OTE","SRA"))

@@

#Fit the model
esem_fit_higher_order <- lavaan::cfa(esem_model_higher_order, fscores ,estimator = "WLSMV", mimic = "Mplus", std.lv=T)

@@

rel.esm_ho <- reliability(esem_fit_higher_order , return.total = TRUE)
# # 
# # rel.esm_ho.m <- rel.esm_ho[4,]
# Total scale omega is .74. each factors alpha f1=.54, f2 =.54. omega F1=.44, F2=.30.
